Accuracy and precision of zero-heat-flux temperature monitoring

### 2019-12-05 manuscript/manuscript.Rmd
kableExtra for table because gt was slow to install on binder

---
title: "Accuracy and precision of zero-heat-flux temperature monitoring"
subtitle: A systematic review and meta-analysis
description: "A systematic review and meta-analysis"
# author:
# - name: Aaron Conway
#   affiliation: Peter Munk Cardiac Centre, UHN & Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
#   email: aaron.conway@utoronto.ca
#   url: https://www.aaronconway.info
# - name: Megan Bittner
#   affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
# - name: Dan Phan
#   affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
# - name: Navpreet Kamboj
#   affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
#   email: navpreet.kamboj@mail.utoronto.ca
# - name: Kristina Chang
#   affiliation: Toronto General Hospital, UHN
# - name: Peter Collins
#   affiliation: Toronto General Hospital, UHN
# - name: Elizabeth Tipton
#   affiliation: Department of Statistics, Northwestern University
# - name: Matteo Parotto
#   affiliation: Toronto General Hospital, UHN
# date: "`r Sys.Date()`"
# repository_url: https://github.com/awconway/zhf-review
# twitter:
#   creator: "@aw_conway"
bibliography: Extras/bibliography.bib
csl: Extras/anesthesiology.csl
author:
  - Aaron Conway PhD:
      email: aaron.conway@utoronto.ca
      institute: [PMCC, LBFON, QUT]
      correspondence: true
  - Megan Bittner BSc:
      institute: [LBFON]
      correspondence: false
  - Dan Phan BSc:
      institute: [LBFON]
      correspondence: false
  - Kristina Chang MScN:
      institute: [TGH]
      correspondence: false
  - Elizabeth Tipton PhD:
      institute: [NW]
      correspondence: false
  - Matteo Parotto MD:
      institute: [TGH]
      correspondence: false
institute:
  - PMCC: Peter Munk Cardiac Centre, University Health Network
  - LBFON: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
  - QUT: School of Nursing, Queensland University of Technology (QUT)
  - TGH: Toronto General Hospital, UHN
  - NW: Department of Statistics, Northwestern University
output:
  bookdown::word_document2:
    reference_docx: Extras/manuscript_template.docx
    pandoc_args:
      - --csl=Extras/anesthesiology.csl
      - --lua-filter=Extras/scholarly-metadata.lua
      - --lua-filter=Extras/author-info-blocks.lua
#output: distill::distill_article
params:
  distill: FALSE
  word: TRUE
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(include=FALSE,
                      echo=FALSE, warning=FALSE, message=FALSE)
library(dplyr)
library(ggprisma) # https://github.com/awconway/ggprisma
library(gt)
library(knitr)
library(magrittr)
source("R/loa_maker.R")
source("R/meta.R")
```

@@

```{r table-1, layout="l-page-outset", include=params$distill}
  ma <- list(primary, low_risk, ICU, OT,  NPA,SL, conflict)
names(ma) <- c("Primary", "Low risk studies", "Intensive Care Unit", 
               "Surgery", "Nasopharyngeal", "Sublingual",
               "Studies not funded by industry")
df <- dplyr::bind_rows(ma, .id="Comparison")
df %>% 
  dplyr::rename(" " = Comparison, "Mean bias" = bias_mean, "Variance" = sd2_est, "Tau-squared" = tau_est, "Lower bound for 95% limit of agreement" = LOA_L, "Upper bound for 95% limits of agreement" = LOA_U, "Outer confidence interval for lower 95% limits of agreement" = CI_L_rve, "Outer confidence interval for upper 95% limits of agreement" = CI_U_rve) %>% 
    gt::gt() %>%
  gt::tab_header(
    title = "Table 1. Results of meta-analyses"  )  %>%
  gt::tab_spanner(
    label = "Population limits of agreement",
    columns = gt::vars(
      `Outer confidence interval for lower 95% limits of agreement`, `Outer confidence interval for upper 95% limits of agreement`)
  )
```

>>>>

---
title: "Accuracy and precision of zero-heat-flux temperature monitoring"
subtitle: A systematic review and meta-analysis
description: "A systematic review and meta-analysis"
author:
- name: Aaron Conway
  affiliation: Peter Munk Cardiac Centre, UHN & Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
  email: aaron.conway@utoronto.ca
  url: https://www.aaronconway.info
- name: Megan Bittner
  affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
- name: Dan Phan
  affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
- name: Navpreet Kamboj
  affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
  email: navpreet.kamboj@mail.utoronto.ca
- name: Kristina Chang
  affiliation: Toronto General Hospital, UHN
- name: Peter Collins
  affiliation: Toronto General Hospital, UHN
- name: Elizabeth Tipton
  affiliation: Department of Statistics, Northwestern University
- name: Matteo Parotto
  affiliation: Toronto General Hospital, UHN
date: "`r Sys.Date()`"
repository_url: https://github.com/awconway/zhf-review
twitter:
  creator: "@aw_conway"
bibliography: Extras/bibliography.bib
csl: Extras/anesthesiology.csl
# author:
#   - Aaron Conway PhD:
#       email: aaron.conway@utoronto.ca
#       institute: [PMCC, LBFON, QUT]
#       correspondence: true
#   - Megan Bittner BSc:
#       institute: [LBFON]
#       correspondence: false
#   - Dan Phan BSc:
#       institute: [LBFON]
#       correspondence: false
#   - Kristina Chang MScN:
#       institute: [TGH]
#       correspondence: false
#   - Elizabeth Tipton PhD:
#       institute: [NW]
#       correspondence: false
#   - Matteo Parotto MD:
#       institute: [TGH]
#       correspondence: false
# institute:
#   - PMCC: Peter Munk Cardiac Centre, University Health Network
#   - LBFON: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
#   - QUT: School of Nursing, Queensland University of Technology (QUT)
#   - TGH: Toronto General Hospital, UHN
#   - NW: Department of Statistics, Northwestern University
# output:
#   bookdown::word_document2:
#     reference_docx: Extras/manuscript_template.docx
#     pandoc_args:
#       - --csl=Extras/anesthesiology.csl
#       - --lua-filter=Extras/scholarly-metadata.lua
#       - --lua-filter=Extras/author-info-blocks.lua
output: distill::distill_article
params:
  distill: TRUE
  word: FALSE
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(include=FALSE,
                      echo=FALSE, warning=FALSE, message=FALSE)
library(dplyr)
library(ggprisma) # https://github.com/awconway/ggprisma
library(kableExtra)
library(knitr)
library(magrittr)
source("R/loa_maker.R")
source("R/meta.R")
```

@@

```{r table-1, layout="l-page-outset", include=params$distill}
  ma <- list(primary, low_risk, ICU, OT,  NPA,SL, conflict)
names(ma) <- c("Primary", "Low risk studies", "Intensive Care Unit", 
               "Surgery", "Nasopharyngeal", "Sublingual",
               "Studies not funded by industry")
df <- dplyr::bind_rows(ma, .id="Comparison")
df %>% 
  dplyr::rename(" " = Comparison, "Mean bias" = bias_mean, "Variance" = sd2_est, "Tau-squared" = tau_est, "Lower bound for 95% limit of agreement" = LOA_L, "Upper bound for 95% limits of agreement" = LOA_U, "Outer confidence interval for lower 95% limits of agreement" = CI_L_rve, "Outer confidence interval for upper 95% limits of agreement" = CI_U_rve) %>% 
  kableExtra::kable() %>% 
   kableExtra::add_header_above(c(" ","","","","","","","","","", "Population limits of agreement" = 2)) %>% 
  kableExtra::add_header_above(c("Table 1. Results of meta-analyses" = 12))
```
